Mendelian randomization for causal inference in Genome-wide association studies

### 2022-01-27 mr-review.Rmd
added data
added bib file

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "1/26/2022"
output: 
  - bookdown::word_document2
---

@@

Methods for Mendelian randomization have appeared at a rapid pace since the 
appearance of the first published GWAS.

Now, GWAS and Mendelian randomization for Biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller sample sizes.

@@

# Future Directions

>>>>

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
output: 
  - bookdown::html_document2
  - bookdown::word_document2
---

@@

Methods for Mendelian randomization have appeared at a rapid and accelerating pace since the 
appearance of the first GWAS.

Now, GWAS and Mendelian randomization for Biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller sample sizes.

@@

# Summary and Outlook
